### 2024-06-02 2024-5-13/sections/implementation.tex
NestC benchmark suite

\medskip
\noindent
\emph{NestC benchmark suite.} 
\zhilin{To be cleaned}
This benchmark suite is generated by string fuzzing test tool \textsc{stringfuzz} \cite{stringfuzz} extended with the counting operator. We generate 500 instances of the nesting of counting operators containing the RECL constraint $x\in e_{nest}\wedge x\in e_{sani}\wedge |x|>50$ in each of them, where $e_{nest}\equiv (e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}})^{\{m_4,n_4\}}$ is a regex of the nesting of counting operators and $e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is as RegCoL benchmark suite. Note that $0\leq m_i\leq n_i\leq 20$ for $i\in [4]$ and $e_i$ containing no counting operators for $i\in [3]$ is randomly generated.  We also generate 500 instances of the nesting of counting operators and a complement operator containing the RECL constraint $x\in e_{comp1}\wedge x\in e_{comp2} \wedge x\in e_{sani} \wedge |x|>50$ in each of them, where $e_{comp\{1,2\}}\equiv \overline{e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}}}$ is a regex of the nesting of counting operators and a complement operator, and $e_{sani}$ are as above. Note that $20\leq m_i\leq n_i\leq 1000$ and $e_i$  containing no counting operators for $i\in [3]$ is randomly generated.

>>>>

\medskip
\noindent
\emph{NestC benchmark suite.} 
We generate this benchmark suite by utilizing the string fuzzing tool \textsc{stringfuzz}~\cite{stringfuzz}. Note that \textsc{stringfuzz} is slightly extended by adding the counting operators.
%This benchmark suite is generated by string fuzzing test tool \textsc{stringfuzz} \cite{stringfuzz} extended with the counting operator. 
For the benchmarks that contain the nestings of counting operators, we use the following template
\[x\in e_{nest}\wedge x\in e_{sani}\wedge |x|>50\]
where $e_{nest}$  is of the form 
\[(e_1^{\{m_1, n_1\}}e_2^{\{m_2, n_2\}}e_3^{\{m_3, n_3\}}e_4^{\{m_4, n_4\}})^{\{m_5, n_5\}},\]
such that $0 \leq m_i\leq n_i\leq 20$ for each $i \in [5]$ and $e_i$ contains no counting operators for each $i  \in [4]$,
moreover, 
\[e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}.\]
Based on this template, we generate 500 instances.

For the benchmarks that contain the nestings of counting operators and a complement operator, we utilize the following template
\[x \in e_{comp1} \wedge x \in e_{comp2} \wedge x \in e_{sani} \wedge |x| > 50, \]
where both $e_{comp1}$ and $e_{comp2}$ are of the form $\overline{e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}} e_4^{\{m_4, n_4\}}}$, such that for each $i \in [4]$, $20 \leq m_i\leq n_i\leq 1000$  and $e_i$ contains no counting operators. Note that two regular expressions $e_{comp1} $ and $e_{comp2}$ are introduced to have a better balance between the numbers of satisfiable and unsatisfiable instances.

%We also generate 500 instances of the nesting of counting operators and a complement operator containing the RECL constraint $x\in e_{comp1}\wedge x\in e_{comp2} \wedge x\in e_{sani} \wedge |x|>50$ in each of them, where $e_{comp\{1,2\}}\equiv \overline{e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}}}$ is a regex of the nesting of counting operators and a complement operator, and $e_{sani}$ are as above. Note that $20\leq m_i\leq n_i\leq 1000$ and $e_i$  containing no counting operators for $i\in [3]$ is randomly generated.
